\documentclass{article}

\usepackage{microtype}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{url}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning,fit,backgrounds,calc}
\usepackage{icml2026}

\icmltitlerunning{Iterative Agent-Team Updating for Peer Review}

\begin{document}

\twocolumn[
  \icmltitle{Iterative Agent-Team Updating for Evidence-Grounded Peer Review:\\
  Immutable Track 2 Execution and a 10-Paper Hosted Audit}
  \icmltitlerunning{Iterative Agent-Team Updating for Peer Review}

  \begin{icmlauthorlist}
    \icmlauthor{Anonymous Authors}{anon}
  \end{icmlauthorlist}
  \icmlaffiliation{anon}{Anonymous Institution}
  \icmlcorrespondingauthor{Anonymous Authors}{anonymous@example.com}
  \vskip 0.3in
]

\printAffiliationsAndNotice{}

\begin{abstract}
We present an end-to-end Track 2 workflow with two bounded loops: paper-time
review refinement over immutable evidence, and offline, development-gated
updating of the review agent team's operating state. The persistent loop
iteratively selects train-only changes to rubric weights, score calibration,
and role-separated retrieval memory; it does not fine-tune hosted model
weights. The \texttt{fast-v1} paper-time path uses five base calls---two
extractors, two reviewers, and one chair---plus a conditional two-call
Author--Chair refinement. On a fixed ten-paper public benchmark, it produced
10/10 schema- and evidence-valid reviews in 631.9 seconds with 54 calls and no
retry, failure, or timeout. Its 2.93 MB of serialized requests is an 83.24\%
reduction from a 17.50 MB counterfactual legacy serialization, but misses the
registered 85\% target. A public-paper case study provides diagnostic process
evidence; absent human ratings, neither loop establishes reviewer-quality
improvement.
\end{abstract}

\section{Scope and Contract}

\paragraph{Track 2 boundary.}
Here, Track 2 denotes the review operation itself, not a post-hoc wrapper around
another pipeline. Its input is a final paper in PDF or Markdown and, optionally,
pre-existing evidence such as result files, tables, logs, and code-version
records. It neither edits the paper nor invents experiments. Claims that cannot
be checked from the frozen bundle must be marked evidence-insufficient.

The implementation copies each input into a per-paper workspace, records its
SHA-256, fixes the output path, and writes \path{review-agent.md}. PDF text
extraction is also versioned and hashed. The resulting bundle digest binds the
paper, evidence inventory, instructions, extractor, and output contract.
Only these fixed inputs are visible to the review run. This realizes the
preparation sequence specified in \path{plan.md} and prevents evidence from
being silently added after review.

\paragraph{Output contract.}
The chair returns Summary, Strengths, Weaknesses, Questions for the Authors,
Contribution, Overall Recommendation, Confidence, and Ethics and Limitations.
The machine record additionally carries integer Soundness, Presentation,
Significance, and Originality scores on 1--4 scales, Overall Recommendation on
1--6, and Confidence on 1--5. Python validation rejects missing fields,
out-of-range values, malformed lists, unknown evidence identifiers, and
unregistered contradictions. The Markdown renderer preserves the requested
human-facing sections.

The system is restricted to public papers and author-authorized material. It
must not process confidential submissions or private review discussion, nor
submit generated text as an official review. These boundaries follow ICML's
reviewer, LLM-use, and peer-review ethics policies
~\cite{icml2026reviewer,icml2026llm,icml2026ethics}.

\begin{figure*}[t]
\centering
\begin{tikzpicture}[
  node distance=3mm,
  stage/.style={
    draw=black!55,
    rounded corners=1pt,
    align=center,
    font=\scriptsize,
    minimum height=8mm,
    inner sep=2pt,
    fill=white
  },
  flow/.style={-{Latex[length=1.5mm]}, semithick, draw=black!65},
  refine/.style={flow, draw=orange!85!black},
  deploy/.style={flow, dashed, draw=blue!65!black}
]
% Paper-time Track 2.
\node[stage,text width=19mm] (input)
  {Public paper\\+ existing evidence};
\node[stage,text width=21mm,right=of input] (freeze)
  {Copy, SHA-256,\\agent manifest};
\node[stage,text width=18mm,right=of freeze] (extract)
  {Evidence\\extractors $E_1,E_2$};
\node[stage,text width=21mm,right=of extract] (review)
  {Independent\\reviewers $R_t,R_e$};
\node[stage,text width=17mm,right=of review] (chair)
  {Chair$_0$\\synthesis};
\node[stage,text width=22mm,right=of chair] (output)
  {Schema + evidence\\validated review};
\foreach \a/\b in {input/freeze,freeze/extract,extract/review,review/chair,chair/output}
  \draw[flow] (\a) -- (\b);

\node[stage,text width=20mm,below=4mm of chair,xshift=-11mm] (challenge)
  {Simulated Author\\challenge};
\node[stage,text width=19mm,right=of challenge] (rechair)
  {Chair$_1$\\re-review};
\draw[refine] (chair.south) -- node[left,font=\tiny]{if selected} (challenge.north);
\draw[refine] (challenge) -- (rechair);
\draw[refine] (rechair.east) -| (output.south);

% Offline persistent team-state update.
\node[stage,text width=19mm,below=20mm of input] (cases)
  {Public historical\\train/dev/test};
\node[stage,text width=26mm,right=of cases,fill=orange!12,draw=orange!75!black] (candidate)
  {\textbf{Candidate team state}\\rubric, calibration,\\role-separated memory};
\node[stage,text width=21mm,right=of candidate] (gate)
  {Development gate\\non-regression\\+ three deltas};
\node[stage,text width=21mm,right=of gate] (decision)
  {Accept/reject\\update current\\and best state};
\node[stage,text width=19mm,right=of decision] (plateau)
  {Repeat until\\plateau\\patience};
\node[stage,text width=21mm,right=of plateau,fill=blue!10,draw=blue!60!black] (state)
  {Restore best\\sealed test once\\\texttt{best\_state.json}};
\foreach \a/\b in {cases/candidate,candidate/gate,gate/decision,decision/plateau,plateau/state}
  \draw[flow] (\a) -- (\b);
\draw[refine] (plateau.south) .. controls +(0,-6mm) and +(0,-6mm) ..
  node[below,font=\tiny]{not converged: propose the next train-only candidate}
  (candidate.south);
\draw[deploy] (state.east) |-
  node[pos=.55,right,font=\tiny,align=left]{load only on\\the next run}
  (output.east);

\begin{scope}[on background layer]
\node[fit=(input)(output)(challenge)(rechair),fill=blue!3,draw=blue!25,
  rounded corners=2pt,inner xsep=3mm,inner ysep=4mm] {};
\node[fit=(cases)(state),fill=orange!3,draw=orange!25,
  rounded corners=2pt,inner xsep=3mm,inner ysep=4mm] {};
\end{scope}
\node[anchor=south west,font=\scriptsize\bfseries,text=blue!55!black]
  at ([yshift=4mm]input.north west)
  {Paper-time Track 2: input and persistent state stay frozen};
\node[anchor=south west,font=\scriptsize\bfseries,text=orange!75!black]
  at ([yshift=4mm]cases.north west)
  {Offline agent-team state update loop};
\end{tikzpicture}
\caption{End-to-end workflow and two separated loops. Paper-time refinement
stress-tests and may revise a review without changing its immutable bundle or
persistent state. The offline loop iteratively updates rubric, calibration,
and role-separated retrieval memory, admits candidates through a development
gate, restores the best state, and supplies only the next Track 2 run. This is
an operating-state update: hosted weights, prompts, and team roster remain
fixed.}
\label{fig:workflow}
\end{figure*}

\section{Fast Pipeline and Two Loops}

\paragraph{Five-call base path.}
\texttt{fast-v1} replaces the legacy 19-section extraction and 14-agent fan-out
with two complementary extraction calls. Each returns typed claims,
limitations, equations, experiment facts, and internal contradictions with
stable evidence IDs. Two independent reviewers receive the compact evidence
registry and specialize in technical validity and empirical/reproducibility
checks. A chair consolidates their evidence-linked findings into the strict
review form. In a ten-paper batch, all papers complete the five-call base path
before refinement selection. At most two papers then receive an author-style
challenge and a second chair call. This base-first scheduler bounds cost and
prevents early papers from consuming the refinement budget.

The review-time state contains rubric weights, score calibration, and at most
eight paper-agnostic memory items. Retrieval excludes the current forum and
passes generalized checklists rather than stored reviews or rebuttals. Human
reviews, rebuttals, and decisions are absent from paper-time requests. The
public 20-case ReviewBench--ReviewRebuttal seed
~\cite{reviewbenchdataset,reviewrebuttaldataset} is split by forum into 16
train, two development, and two sealed-test cases. It is used only for a
deterministic integrity/non-regression smoke test; it does not establish
reviewer quality.

\paragraph{Iterative agent-team update.}
Figure~\ref{fig:workflow} makes the persistent update loop explicit. Each
offline iteration proposes a train-only, immutable \texttt{LearningState}
candidate that updates rubric weights, calibration scale/bias, and
role-separated reviewer/author memory. Development non-regression decides
acceptance; quality, behavior, and state deltas drive plateau stopping; the
best state is restored before one sealed-test evaluation. The registered seed
run executed five iterations, selected iteration 1, and stopped after a
three-step plateau. This is an orchestration-level team update, not gradient
training, hosted-model fine-tuning, prompt rewriting, or roster adaptation.
Separately, the paper-time simulated Author--Chair loop can revise only the
current review over frozen evidence; it cannot teach later papers.

\paragraph{Backend isolation.}
The first-class hosted backend invokes Codex CLI 0.144.1 with an explicit
\texttt{gpt-5.6-sol} model~\cite{openaigpt56sol}. Authentication is the local
ChatGPT login rather than a repository API key. Each request runs in an
ephemeral, read-only working directory with interactive and network tools
disabled. A small environment allowlist excludes variables such as
\texttt{OPENAI\_API\_KEY}. JSON Schema constrains model output; Python performs
semantic validation and bounded retry. One global semaphore enforces
concurrency four across papers, while a monotonic hard deadline terminates the
whole process group. Atomic completion markers, content-addressed cache keys,
and JSONL progress records support auditable resume without treating an invalid
response as complete.

\section{Evaluation Protocol}

\paragraph{Frozen benchmark.}
The runtime audit uses the first ten entries of a public paper-only manifest.
No human reviews, rebuttals, decisions, or private evidence are included. The
set overlaps the historical split as eight train and two development forums,
with no sealed-test forum, so it is a systems audit rather than a quality test.
The
manifest SHA-256 begins \texttt{fdfdd199e694}; the selected learned state digest
begins \texttt{fe1a1597e2e7}. The registered configuration is four paper
workers, global Codex concurrency four, two attempts per logical call, a
1,440-second soft deadline, a 1,800-second hard deadline, conditional author
loop, and at most two refinements. The measured run is cold: cache hits are
zero.

We validate (i) all JSON and rendered review schemas, (ii) every cited evidence
ID against its paper registry, (iii) representative maximum request size
relative to extracted paper text, (iv) deadline and call budget, and (v)
historical non-regression within tolerance 0.02. The quality-adjacent audit
counts linked findings and contradictions, but does not label them correct.

\paragraph{Counterfactual baseline.}
For a like-for-like communication estimate, the validator replays the same
papers, state, \texttt{fast-v1} evidence, critiques, and final Markdown through
the legacy request serializers without making model calls. This isolates
request-shape overhead, but it is not a legacy end-to-end latency or quality
measurement. The pre-registered acceptance target is at least 85\% fewer
request bytes than this serialization.

\section{Results}

\begin{table}[t]
\caption{Cold hosted audit on ten public papers.}
\label{tab:main}
\centering
\scriptsize
\setlength{\tabcolsep}{2pt}
\begin{tabular}{@{}lr@{}}
\toprule
Metric & Result \\
\midrule
Schema/evidence-valid reviews & 10/10 \\
Wall time / throughput & 631.9 s / 0.949 papers/min \\
Logical/actual calls & 54 / 54 \\
Retries / failures / timeouts & 0 / 0 / 0 \\
Request / output bytes & 2,932,889 / 378,772 \\
Linked findings / major--fatal & 220 / 97 \\
Max request-to-paper ratio & 1.103 \\
Deadline and call budget & Pass \\
Legacy request estimate & 17,503,551 bytes, 309 calls \\
Request-byte reduction & 83.24\% (85\% target: Fail) \\
\bottomrule
\end{tabular}
\end{table}

Table~\ref{tab:main} reports the run identified by the immutable input
manifest, pipeline digest, state digest, model, and CLI version. Fifty calls
served the base paths and four served the two selected refinements. All 220
finding/contradiction links resolved to registered evidence, including 97
items marked major or fatal by the generated records. This is a traceability
count, not 97 independently verified defects.
Byte counts are UTF-8 serialized backend payload and output sizes, not token
usage, network transfer, or billing measurements.

\begin{table}[t]
\caption{Concurrent per-call hosted latency in seconds. Refinement stages have
two calls; durations are not additive wall time.}
\label{tab:latency}
\centering
\small
\setlength{\tabcolsep}{6pt}
\begin{tabular}{@{}lrr@{}}
\toprule
Stage & p50 & p95 \\
\midrule
Evidence extraction & 51.93 & 60.36 \\
Consolidated review & 38.00 & 42.10 \\
Chair/final review & 30.72 & 38.60 \\
Author challenge & 43.15 & 46.67 \\
\bottomrule
\end{tabular}
\end{table}

The representative request ratio of 1.103 is below the registered ceiling of
3, and the run finished in 35.1\% of the hard deadline. The counterfactual
legacy serializer would issue 309 calls and 17.50 MB of requests. The observed
83.24\% byte reduction is large but 1.76 percentage points below the 85\%
criterion; the overall acceptance audit therefore fails. Reducing shared
schema and context repetition is the remaining measurable optimization.

\paragraph{Historical smoke.}
State build run \texttt{3842327ddf72639976d7} preserved development MAE at
0.7083 while Brier changed from 0.2863 to 0.2796. The one-time, two-forum sealed
test reported MAE 0.3750 and Brier 0.1229. With only two development and two
test forums and deterministic proxy reviews, these numbers verify state
selection, role separation, and non-regression plumbing only.

\section{Public-Paper Case Study}

We separately ran the same Track 2 workflow on public paper
\texttt{2602.00521v2}; its PDF SHA-256 begins \texttt{6c29c6497761} and bundle
digest begins \texttt{bfacf0180851}. Seven hosted calls completed in 220.2
seconds with no retry, failure, timeout, or cache hit, using 565,696 request
bytes and 49,823 output bytes. The final scores were Soundness 1, Presentation
2, Significance 3, Originality 3, Overall Recommendation 2, and Confidence 4.
Refinement retained these scores and continued to mark the review as needing
refinement.

The final review identified a central latent-scale comparability problem in
independently fitted human and LLM graded-response models; an equation
denominator and undefined boundary cases; inconsistent threshold counts;
gate inequalities and Phase-2 application mismatches; a prompt/JSON score-scale
mismatch; and missing bootstrap unit and multiplicity specifications. These
findings demonstrate that the evidence registry can support concrete,
cross-section criticism. They were not adjudicated by the authors or blinded
human reviewers, and some detailed table cross-checks were still missed.
Accordingly, the case study is inspectable process evidence, not a precision,
recall, or superiority result.

\section{Limitations and Reproducibility}

The benchmark is small, public-only, and contains revised paper text; RecSys is
not represented in the historical seed. Hosted model behavior and service
latency can drift. The byte baseline reuses \texttt{fast-v1} intermediate
outputs and therefore estimates legacy serialization rather than executing the
legacy model pipeline. Evidence-ID validity establishes referential integrity,
not factual correctness. No human annotation, inter-rater agreement, blinded
comparison, review usefulness score, robustness suite, model ablation, or cost
measurement was performed. Confidential-review suitability is explicitly out
of scope. The case-study manifest omits its source URI, so its public
provenance is not independently attested by that artifact and should be added
before external release.

All reported values are generated artifacts rather than transcribed logs. The
benchmark manifest, per-paper Track 2 bundles, progress records, reviews, run
summary, acceptance audit, and human inspection sheet are under
\path{artifacts/benchmark_fast_v1/gpt-5.6-sol-cold}. The case-study review is
under \path{artifacts/track2/2602.00521v2-loop2}. The report builds with
\texttt{make -C report check}. Formatting follows the ICML 2026 author style
~\cite{icml2026author}; it does not imply submission or endorsement.

\paragraph{Conclusion.}
\texttt{fast-v1} establishes a reproducible Track 2 path from immutable public
input to evidence-linked structured review, while the dev-gated offline loop
provides a versioned mechanism for repeatedly updating the agent team's
operating state. The ten-paper run met schema, traceability, deadline,
reliability, context-size, and historical non-regression checks. It did not
meet the 85\% request-byte reduction target, and neither loop yet supports a
claim of improved reviewer quality.

\clearpage
\bibliographystyle{icml2026}
\bibliography{references}

\end{document}
